---
title: "Keeping track of running code"
output: html_document
---



The first point of this post is to give a simple way to check whether code is still running or has hung.

`tail -f output_file` 

will keep running the tail command line utility on `output_file` and update itself as new lines are written. Where `output_file` here could be a logfile.

Another similar approach is to use `wc -l filename` which will use word count to give the number of lines present in a file and can be useful to see the status of writing out data.


## Publishining to Wordpress from Rmarkdown

The second point of this post is to test out an automated way of posting from Rmarkdown to a wordpress site using the *RWordPress* package. 


To be clear, while the code is presented below in a *knitr* chunk, I find it easier to run it as a script seperately after knitting the .Rmd document to html (I'll probably functionalise this at some stage).

> The Rmarkdown file here is saved as tail.Rmd

```{r setup, eval=FALSE, echo=TRUE}

# install required packages
if (!require('knitr')) {
  install.packages("knitr")
}
if (!require('devtools')) {
  install.packages("devtools")
}
if (!require('RWordPress')) {
  devtools::install_github(c("duncantl/XMLRPC", "duncantl/RWordPress"))
}

# Give the user name, password, and URL for the WordPress site.
options(WordpressLogin = c(user = 'password'),
        WordpressURL = 'http://[url]/xmlrpc.php')


```

`user` is the wordpress login username (unquoted).

`password` is the password for the site (quoted).

`[url]` is the sites URL either in the format of **mysite.com** or **mysite.wordpress.com**.



```{r publish, eval=FALSE, echo=TRUE}

library(RWordPress)
library(knitr)

knit2wp('path_to_file/tail.Rmd',
        title = 'Keeping track of running code',
        categories = c('Tools','R'), publish = FALSE )

```


`categories = c('Tools', 'R')` will only work if the categories listed have already been created.

`publish` is set to FALSE to allow me to review the post before it is published.


More information on how to do this can be found [here](https://www.r-bloggers.com/create-blog-posts-from-rstudio-to-wordpress/) and [here](http://sites.tufts.edu/emotiononthebrain/2017/08/12/blog-posting-from-r-markdown-to-wordpress/).



